---
title: "Capstone project"
author: "Dinesh Rajan R A"
date: "01/05/2021"
output:
  html_document:
    df_print: paged
---

####################################### Implementation #######################################

# > Understand kmeans clustering.
# > Understand retail Data for applying kmeans clustering.
# > Understand the objective.
# > Maths of kmeans clustering.
# > understand Optimum number of cluster.
# > Using elbow method to determine the optimal number of cluster.
# > model fitting
# > Evaluation

# > Objective

# The client is a leading Fashion retailer in Australia. Company runs a display advertising campaign for this brand, where it shows ads to users leading them to make a purchase on the brands website.The given dataset is the Sales data for all users who made a purchase online in the first half of October '17.

# Based on your analysis, arrive at a statistical segmentation of the brands audience based 
# on Revenue. The number of segments is up to you. Please provide definitions of each groups

# > desired Library installation

```{r}
# install.packages("factoextra")
# install.packages("rpivotTable")
# install.packages("cluster")
# install.packages("fpc")
# install.packages("factoextra")
# install.packages("rpivotTable")
# install.packages("ggplot2")
# install.packages("dplyr")
# install.packages("magrittr")
```


```{r include=FALSE}
library(ggplot2)
library(dplyr)
library(magrittr)
library(cluster)
library(fpc)
library(factoextra)
library(rpivotTable)
```

# > Setting working directory

```{r}
getwd()

path = "C:/Users/DELL/Downloads/Capston Project 1"
#setwd(path)
```

# > reading data

```{r}
revenue = read.csv('RevenueCluster.csv',header = TRUE)
head(revenue,10)
```

# > subsetting/manipulating data to fit kmeans clustering

```{r}
D = subset(revenue,select = 5)
head(D,10)
```

# > fitting basic model taking a random number of cluster say "3"

```{r}
set.seed(100)
basicmodel = kmeans(D,3)
basicmodel$tot.withinss
basiccluster = basicmodel$cluster
head(basiccluster)
```

# > calculating optimum number cluster

```{r}
optimcluster <- function(k){
  cluster <- kmeans(D, k)
  return(cluster$tot.withinss)
}

wss <- sapply(1:20, optimcluster)

optimK <- data.frame(k = 1:20, wss)
head(optimK)
```

Interpretation: The method consists of plotting the explained variation as a function of the number of clusters, and picking the elbow of the curve as the number of clusters to use.

### ploting the k value from 1 to 20 against within sum of square (wss)

```{r}
ggplot(data = optimK) + aes(x=k, y= wss) + geom_point() + geom_line()+
  scale_x_continuous(breaks = seq(1,20,by = 1))

OptimunCluster <- "Enter a number which is optimum for Analysis"
```

# > Model fitting using optimum k

```{r}
model = kmeans(D,3)
cluster = model$cluster
```


```{r}
mapping = data.frame(revenue = D, cluster = cluster)
write.csv(mapping,'mapping.csv')
```

